### 2024-03-04 doc/15yrsChange.Rmd
Update 15yrsChange.Rmd
worked on second paragraph results section

## Paragraph discussing constituent fluxes of net biomass change - across the whole plot & within regions
The trend in net woody production can be explained by its constituent fluxes (Figure 3). Trends in woody mortality show that for the first two census intervals, the whole plot has lost **VALUE** and then **VALUE** Mg C/ha/year, increasing to a loss of **VALUE** Mg C/ha/year for the most recent census interval (Figure 3b). Woody productivity contributes positively to the flux, showing that the whole plot gained **VALUE** Mg C/ha/year in the first interval, **VALUE** Mg C/ha/year in the second, and **VALUE** Mg C/ha/year in the third (Figure 3c). Areas of low deer, low nuisance species were consistently the most productive ending at **VALUE** Mg C/ha/year in the interval 2018 to 2023, and areas of high deer, high nuisance species were the least productive at **VALUE** Mg C/ha/year in the interval 2018 to 2023.

>>>>

## Paragraph discussing constituent fluxes of net biomass change - across the whole plot & within regions
The trend in net woody production can be explained by its constituent fluxes (Figure 3). Trends in woody mortality show that for the first two census intervals, the whole plot has lost **VALUE** and then **VALUE** Mg C/ha/year, increasing to a loss of **VALUE** Mg C/ha/year for the most recent census interval (Figure 3b). Woody productivity contributes positively to the flux, showing that the whole plot gained **VALUE** Mg C/ha/year in the first interval, **VALUE** Mg C/ha/year in the second, and **VALUE** Mg C/ha/year in the third (Figure 3c). Areas of low deer, low nuisance species were consistently the most productive ending at **VALUE** Mg C/ha/year in the interval 2018 to 2023, and areas of high deer, high nuisance species were the least productive at **VALUE** Mg C/ha/year in the interval 2018 to 2023. Recruitment has consistently added smaller magnitude amounts of carbon with the whole plot gaining **VALUE** Mg C/ha/year (Figure 3d). Recruitment was highest at **VALUE** Mg C/ha/year in areas with high deer and high vulnerable species, and lowest at **VALUE** Mg C/ha/year in areas with high deer and low vulnerable species.
